\paperTitle

### 2014-05-13 doc/icml2014/undirected.tex
gotten up to lemma 2
new asymptotic analysis comparing pi and cl - something is wrong

% DONE: need more of a transition from previous sections
Recall that we used tensor factorization and composite likelihood
to estimate the hidden marginals $Z_\sC = \BP(\vh_\sC)$ and $\mOpp{v}{i} = \BP(x_v \mid h_i)$.
For directed models, obtaining the local conditional tables from $Z_\sC$ requires
renormalizing $Z_\sC$.
For undirected log-linear models, the parameters cannot simply be obtained locally;
we will have to perform global optimization.
Fortunately, we will show that this optimization problem is convex
by relating the recovered conditional moments with the expected features of
the log-linear model.

% Define model
As before, let $\sG$ be a graphical model with observed variables $X$ and hidden variables $H$
(see \figureref{examples-mrf} for an example).
For each clique $\sC \in \sG$, we have a feature vector $\phi_\sC(\vx_\sC, \vh_\sC)$,
where $\vx_\sC$ and $\vh_\sC$ are the observed and hidden variables in $\sC$, respectively.
Let $\phi(\vx, \vh) = \sum_{\sC \in \sG} \theta^\top \phi_\sC(\vx_\sC,\vh_\sC)$ be the global feature vector.
We consider log-linear models of the following form:
\begin{align}
p_\theta(\vx, \vh) &= \exp\left( \theta^\top \phi(\vx,\vh) - A(\theta) \right),
\end{align}
where $A(\theta) = \sum_{\vx, \vh}  \exp( \sum_\sC \theta^\top \phi(\vx,\vh) )$ is the log-partition function.

@@

The pseudolikelihood also replaces the log-partition function $A(\theta)$
with a sum over the variables in the neighbourhood: $A_a(\theta; x_{\sN(a)}) = \sum_{a' \in \{a\} \union \sN(a)} \exp(\theta^\top\phi_{\sN(a)}(a'))$,
which cannot be computed from just the hidden clique marginals $Z_\sC$,
since the neighbors $\sN(a)$ in general do not form a clique.
We adapt our earlier algorithm ($\LearnClique$) to estimate the
  marginals over all neighborhoods $Z_{\sN(a)}$ by noting that
  \lemmaref{bottleneck-views} guarantees exclusive views for any connected
  sub-graph of $\sG$, not just cliques.

>>>>

% DONE: need more of a transition from previous sections
Recall that we used tensor factorization and composite likelihood
to estimate the hidden marginals $Z_\sC = \BP(\vh_\sC)$ and $\mOpp{v}{i} = \BP(x_v \mid h_i)$.
For directed models, obtaining the local conditional tables from $Z_\sC$ simply requires
renormalizing $Z_\sC$.
For undirected log-linear models, the canonical parameters cannot be obtained
locally.
Fortunately, we can construct a convex optimization problem
by relating the recovered conditional moments with the expected features of
the log-linear model.

% Define model
As before, let $\sG$ be a graphical model with observed variables $X$ and hidden variables $H$
(see \figureref{examples-mrf} for an example).
For each clique $\sC \in \sG$, we have a feature vector $\phi_\sC(\vx_\sC, \vh_\sC)$,
where $\vx_\sC$ and $\vh_\sC$ are the observed and hidden variables in $\sC$, respectively.
Let $\phi(\vx, \vh) = \sum_{\sC \in \sG} \theta^\top \phi_\sC(\vx_\sC,\vh_\sC)$ be the global feature vector.
We consider log-linear models of the following form:
\begin{align}
p_\theta(\vx, \vh) &= \exp\left( \theta^\top \phi(\vx,\vh) - A(\theta) \right),
\end{align}
where $A(\theta) = \log \sum_{\vx, \vh}  \exp( \theta^\top \phi(\vx,\vh) )$ is the log-partition function.

@@

The pseudolikelihood also replaces the log-partition function $A(\theta)$
with a sum over the variables in the neighbourhood: $A_a(\theta; x_{\sN(a)}) = \sum_{a' \in \{a\} \union \sN(a)} \exp(\theta^\top\phi_{\sN(a)}(a'))$,
which cannot be computed from just the hidden clique marginals $Z_\sC$,
since the neighbors $\sN(a)$ in general do not form a clique.
We adapt our earlier algorithm ($\LearnClique$) to estimate the
  marginals over all neighborhoods $Z_{\sN(a)}$ by noting that
  \lemmaref{bottleneck-views} guarantees exclusive views for any connected
  subgraph of $\sG$, not just cliques.
